Implementation of a lattice Boltzman method for immiscible multiphase flow simulations using the level set method

### 2015-11-02 Paper/scifile.tex
Cover Letter - Erster Entwurf

\author
{Lorenz Hufnagel,$^{1}$ Daniel Zint,$^{1}$\\
\\
\normalsize{$^{1}$Chair for System-Simulation, Friedrich Alexander Univerität Erlangen-Nürnberg}\\
\normalsize{91058 Erlangen, Germany}\\ % ist das so richtig?
\\
%\normalsize{$^\ast$To whom correspondence should be addressed; E-mail:  jsmith@wherever.edu.}
}

@@

\begin{sciabstract}
  We implemented the lattice Boltzman method for immiscible multiphase flow simulations. We combined this with the level set method according to the paper of G. Thömmes FUSSNOTE. After reimplementing the testcases mentioned in the paper, we studied the coupling of the two methods and the impact of the variables.
\end{sciabstract}

@@

\newpage
Hier folgen Informationen über das Stylesheet. Sollten wir dann irgendwann loeschen, fand ich aber fuers erste ganz hilfreich.

>>>>

\author
{Lorenz Hufnagel,$^{1}$ Daniel Zint,$^{1}$\\
\\
\normalsize{$^{1}$Chair for System-Simulation, Friedrich Alexander Univerit\"at Erlangen-N\"urnberg}\\
\normalsize{91058 Erlangen, Germany}\\ % ist das so richtig?
\\
%\normalsize{$^\ast$To whom correspondence should be addressed; E-mail:  jsmith@wherever.edu.}
}

@@

\begin{sciabstract}
  We implemented the lattice Boltzmann method for immiscible multiphase flow simulations and combined it with the level set method according to the paper of G. Thömmes FUSSNOTE. The level set method is used to calculate the movement of the interface between the two phases. The input for the level set method is computed by the lattice Boltzmann method. We reimplemented the test cases, mentioned in the paper, to study the method-coupling and its impact on accuracy.
\end{sciabstract}

@@

\newpage
Hier folgen Informationen \"uber das Stylesheet. Sollten wir dann irgendwann l\"oschen, fand ich aber f\"urs erste ganz hilfreich.
